---
title: "Tweet_analysis"
output: html_notebook
---
```{r load required libraries}

# library for interaction with twitter API
library(rtweet)

# library for natural language processing
library(tidyverse)
library(tidytext)
library(tm)
library(qdap)

# libraries for graphic representation
library(mapproj)
library(maps)
library(ggthemes)
library(ggwordcloud)
library(gridExtra)

# library for LDA model
library(topicmodels)

```


```{r}

# The script performs an iterative tweet collection based on keywords. 
# The data are stored in RData files referenced in a master file.
# Data are reloaded to perform geographic localization, word association and topic modeling 

# initialize twitter API access
access = read.csv("cred.csv", header = TRUE, stringsAsFactors = FALSE)

key = access$key
secret = access$secret

access_token = access$access_token
access_secret = access$access_secret

appname = access$appname

twitter_token <- create_token(
  app = appname,
  consumer_key = key,
  consumer_secret = secret,
  access_token = access_token,
  access_secret = access_secret)

rm(key, secret, access_token, access_secret, appname)

```


```{r iterative tweet collection}
#The twitter API limit tweet collect to 18000/15 min, launching request for millions of tweets is not indicated as an interruption of the connection might derail the whole process. Here the code takes advantage of the max_id argument to search tweet older than the oldest tweet from the previous request. At each iteration, approx 18000 tweets are selected and saved in separate RData files.

#The names of the collected files are stored in a master file for easy subsequent loading.

# give the project a name
proj_name = "pharma_project"

# the Id of the most recent tweet can be manually updated, otherwise, leave NA
# the number of iteration is set by max_iter
data_file_names = list()
max_id = NA
max_iter = 4
my_keyword = "pharma"
include_retweets = FALSE

data_file_names[[1]] = paste("search terme:", my_keyword, " date :", Sys.Date(), " include_retweets:", include_retweets)

for (i in c(1:max_iter)){
  
  list_tweet <- search_tweets(q = my_keyword,
                               n = 18000, #18000,
                               lang = "en",
                               include_rts = include_retweets,
                               retryonratelimit = TRUE,
                               type = "recent",
                               max_id = max_id)
  
  max_id = list_tweet$status_id  %>% sort(decreasing = F) %>% head(1) %>% as.character()

  save(list_tweet, file = paste(proj_name,"-tweets-",i,".RData", sep = ""))
  
  data_file_names[[i+1]] = paste(proj_name,"-tweets-",i,".RData", sep = "")
  
} 

tweets_file = paste("master_file-",proj_name,"-",Sys.Date(),".csv", sep ="" )

write.csv(unlist(data_file_names), file = tweets_file)
print(paste("file names saved in: ",  tweets_file))

rm(twitter_token)

```



```{r plot collected tweets}

# sequentially load the data 
# to plot the geographic coordinates of tweets
# typically less than 10% of the tweets have associated geographic coordinates
list_of_tweet_file = read.csv(tweets_file, header = T) %>% select(x) 

my_tweets = list()

for (i in c(2:nrow(list_of_tweet_file))){
  
  p = as.character(list_of_tweet_file[i,1])
  
  load(p)
  
  my_tweets[[i]] = list_tweet
  rm(list_tweet)
  
}

my_tweets = do.call(rbind, my_tweets)
head(my_tweets)

# extract coordinates, eliminate tweets without coordinates and plot location
# WARNING generally, only 1% of the tweets have an associated geographic localisation
plot_map <- my_tweets %>% lat_lng() %>% select(lat,lng) %>% drop_na() %>%
  ggplot(aes(x = lng, y = lat))+
  borders("world", colour = "white", fill = "gray90", size = .2) +
  theme_map()+
  geom_point(alpha = .5, size = 1, color = "#B99364")+
  labs(title = "tweets localisation", caption = paste(list_of_tweet_file[1, ], sep = ""), color = "topic")

plot_map

```


```{r}

# Save image of the map

png(file = paste(proj_name,"-",Sys.Date(),"-plot_map.png", sep = ""), res = 200, width = 1000, height = 800)
plot_map
dev.off()
```



```{r}
# change column name to "doc_id" and "text", as required by text mining functions.
my_tweets_txt <- my_tweets %>% mutate(doc_id = status_id, text =my_tweets$text)
head(my_tweets_txt)
```


```{r raw word frequency}

# calculate word frequency
word_freq <- my_tweets_txt %>% 
                unnest_tokens(output=word, 
                input="text", 
                token="words", 
                format="text") %>% 
                count(word)

# rapid sanity check of words frequency. 
word_freq %>% top_n(40,n) %>%
          ggplot(aes(x = reorder(word,n), y = n))+
          geom_point()+
          labs(x = "word", y = "count")+
          coord_flip()+
          theme_minimal()

```


```{r clean word frequency}

# make corpus
# clean the corpus (put everything to lower case, replace curly ', remove stop words, remove punctuation, remove again stop words after punctuation removal)
# stem words to aggregate similar termes
# create a term-document matrix (TDM), eliminate rare words 
# measure words frequency and plot

# create corpus
my_tweets_corpus <- data_frame(doc_id = my_tweets_txt$status_id, text =my_tweets_txt$text)

# convert to VCopus type for subsequent analysis 
source_df <- DataframeSource(my_tweets_corpus)
corpus_df_init <- VCorpus(source_df)
rm(source_df)

# clean text and remove stop words
corpus_df <-  corpus_df_init %>%  
              tm_map(content_transformer(tolower)) %>%
              tm_map(content_transformer(function(x) gsub(x, pattern = "’", replacement = "'"))) %>%
                            tm_map(removeWords, c(stopwords("en"))) %>%
                            tm_map(removePunctuation) %>%
                            tm_map(removeWords, c(stopwords("en")))

# Stem words to regroup words of the same family (ex: appoval, approving => approv)
corpus_df_stem = tm_map(corpus_df, stemDocument)

# create TDM: count of word in each element od the corpus (tweets)
my_TDM <- TermDocumentMatrix(corpus_df_stem)

# remove sparse termes to reduce memory footprint
my_TDM_r <- removeSparseTerms(my_TDM, sparse = 0.98)
freq <- rowSums(as.matrix(my_TDM_r)) %>% 
        as.data.frame()  %>% 
        rownames_to_column() %>% 
        rename(c(freq_word = . , word = rowname))


# reconstitute truncated words
freq$word_comp = freq$word %>% stemCompletion(corpus_df, type = "prevalent")

# plot frequent words
freq %>%  ggplot(aes(x = reorder(word_comp,freq_word), y = freq_word))+
          geom_point()+
          coord_flip()+
          labs(x = "", y = "word frequency")+
          theme_minimal()+
          labs(title = "words associated with \"pharma\"")

```
```{r}

# display frequent words as a wordcloud
freq %>% arrange(-freq_word) %>% slice_tail(n = nrow(freq)-1)%>%
  
  ggplot(aes(label = word_comp, size = freq_word, color = freq_word))+
                  geom_text_wordcloud(eccentricity = 1)+
                  theme_minimal()+
                  labs(title = "words associated with \"pharma\"", caption = paste(list_of_tweet_file[1, ], sep = ""))

```
As expected, the "Big Pharma" expression made its way to twitter. With the word "big" being the most frequently associated with "pharma"

```{r word association}

# search for word associated with selected words ("my_termes") in the stemmed corpus
# The goal is to gain more insight into the current news about some major pharma companies
my_termes = c("pfizer","teva","moderna")

# find associated words. This can take a couple of minutes
word_assoc <- findAssocs(my_TDM, my_termes, 0.1)
head(word_assoc)

word_assoc_vec <- list_vect2df(word_assoc, col2 = "word", col3 = "assoc") %>% rename(term = X1)

word_assoc_vec$word_comp = word_assoc_vec$word %>%
                          stemCompletion(corpus_df, type = "prevalent")

print(word_assoc_vec)


```

```{r}

# plot the graph and the wordcloud of the word most commonly associated with "my_termes"

plot_cloud = list()
j = 1

for (i in my_termes){
  
  x = word_assoc_vec %>% filter(term == i)
  x_top_10 = x %>% arrange(desc(assoc)) %>% slice(1:7)
  print(x_top_10)
  
  plot_cloud[[j]] <-  x_top_10 %>% 
                      ggplot(aes(x = word_comp, y = assoc, color = assoc))+
                      geom_point(show.legend = FALSE)+
                      coord_flip()+
                      labs(title = as.character(i))+
                      xlab("")+
                      ylab("word association")+
                      theme_minimal()
  
  j = j + 1
  
  
  plot_cloud[[j]]  <- x_top_10 %>% 
                      ggplot(aes(label = word_comp, size = assoc, color = assoc))+
                      geom_text_wordcloud(eccentricity = 10)+
                      theme_minimal()
  
  j = j + 1
  
}

grid.arrange(grobs = plot_cloud, ncol = 2)

```
At the time of the analysis, it was revealed that Pfizer leaked the private medical data of some prescription drug users. Teva announced its collaboration wih Onica for its digital health platform (digihaler). Moncef Slaoui, former Moderna Board Member, is planning to sell its shares, as the company is working on a covid-19 vaccine.


```{r LDA topic modeling}
# perform a topic modeling analysis using Latent Dirichlet Allocation
# The goal is to observe if tweets can be classified into coherent topics.

# prepare data as DTM
my_DTM <- DocumentTermMatrix(corpus_df_stem)

# If the sparse terms are not removed before the transformation to matrix, the memory of the computer might be insufficient.
my_DTM_r <- removeSparseTerms(my_DTM, sparse = 0.98)
glimpse(my_DTM_r)

# remove documents without entries (required for LDA algorithm)
rowTotals = apply(my_DTM_r , 1, sum)
my_DTM_r = my_DTM_r[rowTotals> 0, ]
glimpse(my_DTM_r)

# perform modeling
mod <- LDA(x=my_DTM_r, k=3, method="Gibbs", control=list(alpha=1, delta=0.1, seed=111))

# extract the beta matrix 
LDA_res = tidy(mod, matrix="beta")

# reconstitute stemmed words
LDA_res$term_comp = LDA_res$term %>% stemCompletion(corpus_df, type = "prevalent")


# plot a wordcloud of the most representative words of each topics
LDA_res %>% ggplot(aes(label = term_comp, size = beta, color = topic)) +
            geom_text_wordcloud(eccentricity = 10)+
            theme_minimal()+
            facet_wrap(.~topic, ncol = 2)

```

If the tweets are distributed in 3 topics, the first one seems focused on the industry (keywords: health, company, medic, drug, market), the second one the opioid crisis (keywords: purdu, oxycontin, criminal, opioid, charges) and the third one revolves around the covid-19 crisis (keywords: vaccine, people, covid19, money, Trump)

```{r}
# perform sentiment analysis on words representative of different topics

# load sentiment lexicon
library(textdata)
lex_sent = get_sentiments("afinn")
lex_sent$stem = lex_sent$word %>% stemDocument()


left_join(LDA_res, lex_sent, by = c("term" = "stem")) %>% 
  mutate(score = beta *value) %>% 
  group_by(topic) %>% 
  summarize(sentiment = sum(score, na.rm = TRUE)) %>% 
  ggplot(aes(x = topic, y = sentiment))+
  geom_col(fill = "lightgrey")+
  theme_minimal()+
  coord_fixed(ratio = .5)


```
Topics 1 and 3 have a rather positive connotation, while topic 2 is, on average, associated with negative terms.

```{r}
# display tweets topic in function of geographic coordinates

# identify tweets with available geographic coordinates
NA_loc = my_tweets %>% lat_lng() %>% select(lat,lng) %>% is.na()
NA_loc_tot = !NA_loc[,1] & !NA_loc[,2] 
topics_loc = topics(mod)[NA_loc_tot]

# mark tweets localization with one color/topic
plot_map_topics = my_tweets %>%
  lat_lng() %>%
  select(lat, lng) %>%
  drop_na %>%
  mutate(topics_loc = topics_loc) %>%
  ggplot(aes(
    x = lng,
    y = lat,
    color = as.factor(topics_loc)
  )) +
  borders("world",
          colour = "black",
          fill = "gray90",
          size = .2) +
  theme_map() +
  geom_point(alpha = 1) +
  theme(legend.position = "top") +
  scale_color_economist() +
  labs(title = "tweets localisation", caption = paste(list_of_tweet_file[1, ], sep = ""), color = "topic")

plot_map_topics

```

```{r}
# display tweets topic in function of geographic coordinates in the US

my_tweets %>%
  lat_lng() %>%
  select(lat, lng) %>%
  drop_na %>%
  mutate(topics_loc = topics_loc) %>%
  ggplot(aes(
    x = lng,
    y = lat,
    color = as.factor(topics_loc)
  )) +
  borders("state",
          colour = "black",
          fill = "gray90",
          size = .2) +
  coord_map(ylim = c(20,50), xlim = c(-70,-130))+
  theme_map() +
  geom_point(alpha = 1) +
  theme(legend.position = "top") +
  scale_color_economist() +
  labs(title = "tweets localisation", caption = paste(list_of_tweet_file[1, ], sep = ""), color = "topic")



```





